---
title: "Shopify Intern"
author: "Junwei Hu"
date: "5/13/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1

## When I first looked at the AOV, it's too large so I thought it might be miscalculated, or there might be some missing values or wrong values in the data. Then I looked at the dataset and did some saummary and calculation

```{r}
data <- read.csv("2019 Winter Data Science Intern Challenge Data Set - Sheet1.csv")
head(data)

attach(data)
```

## Recalculate the AOV by diving the total amount by the total items

```{r}
total_amount = sum(data$order_amount)
total_item = sum(data$total_items)

new_AOV = total_amount / total_item
new_AOV

```

## $357.92 sounds much better than $3145.13 for AOV, but it is still kind high for "relatively affordable sneakers"
## Next I will dig into each shop to see if there is any wrong values

```{r}
library("dplyr")

shop_average <- data %>%
  group_by(shop_id) %>%
  summarise(total_amount = sum(order_amount),
            total_item = sum(total_items)) %>%
  transmute(shop_id = shop_id,
            shop_average = total_amount/total_item) %>%
  arrange(desc(shop_average))

shop_average

```

```{r}
boxplot(shop_average$shop_average, ylab = "AOV per Shop", 
        horizontal = TRUE)

```

## So from the table and the plot above, there are two outliers, shop 78 with AOV 25725 and shop 42 with AOV 352
## But I feel like 352 could be reasonable so there must be something wrong with shop 78
## Then exclude shop 78 and calculate the AOV again

```{r}

mean(shop_average[shop_average$shop_id != 78,]$shop_average)


```

```{r}
median(shop_average$shop_average)

```
```{r}
tab <- table(shop_average$shop_average)
names(tab[tab == max(tab)])

```

## I calculated the new AOV after removing shop 78, which is $152.26
## But before we figure out what happeed to shop 78, it is not appropriate to just remove shop 78
## So I calculate the median value of the AOV, which is $153
## And also the mode value, the most common AOV, which is also $153


## I would report mode value of AOV since it is the most common value of all the shops
## And the value is $153




# Question 2








